---
title: "example_GetSamenMetenData"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example_GetSamenMetenData}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(samanapir)
```

# Get the sensors of a municipality
You can use the function 'GetSamenMetenAPIinfoMuni' to obtain for a particular
municipality, all the sensors and their meta information. The meta
information contains the name (kit_id), the location(lat, lon), some names of
the reference stations. A second dataframe is returned including information
about which parameters are measured, their units and the url to the
observations.

NOTE: the input for the function is the code of the municipality, as a string.

```{r municipality}
# Example 1: municipality
muni_code <- "200"
muni_data_example_1 <- GetSamenMetenAPIinfoMuni(muni_code)

# Example 2: error in input
muni_code <- 200
muni_data_example_2 <- GetSamenMetenAPIinfoMuni(muni_code)

# # Example 3: error in unknown municipality
# muni_code <- "908354" 
# muni_data_example_3 <- GetSamenMetenAPIinfoMuni(muni_code)

```
# Get the sensors of a project
You can use the function 'GetSamenMetenAPIinfoProject' to obtain for a particular
project, all the sensors and their meta information. The meta
information contains the name (kit_id), the location(lat, lon), some names of
the reference stations. A second dataframe is returned including information
about which parameters are measured, their units and the url to the
observations.

NOTE: the input for the function is the name of the project, as a string.

An overview of all the projectnames can be found in the github for Samen Analyseren Tool

```{r project}
# Example 1: project
project_name <- "HEI"
project_data_example_1 <- GetSamenMetenAPIinfoProject(project_name)

# Example 2: error input
project_name <- 200
project_data_example_2 <- GetSamenMetenAPIinfoProject(project_name)

# # Example 2: error unknown project
# project_name <- "hei"
# project_data_example_2 <- GetSamenMetenAPIinfoProject(project_name)

```
