---
title: "example_GetSamenMetenData"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example_GetSamenMetenData}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(samanapir)
```

# Introduction

The sensor data from [Samen Meten][https://samenmeten.rivm.nl/dataportaal/] can
be obtained using an API. This package contains functions to use this API. First
part is to get the sensors in a particular project or municipality and their
meta-data. Second get the observations of 1 parameter of the sensor for a
particular time period.

For more information about the API see: [API Samen Meten][https://www.samenmetenaanluchtkwaliteit.nl/dataportaal/api-application-programming-interface]

## Get the sensors of a municipality
You can use the function 'GetSamenMetenAPIinfoMuni2' to obtain for a particular
municipality, all the sensors and their meta information. The meta
information contains the name (kit_id), the location(lat, lon), some names of
the reference stations. A second dataframe is returned including information
about which parameters are measured, their units and the url to the
observations.

NOTE: the input for the function is the code of the municipality, as a string.
NOTE: If connection with API was succesful, but no data available, then an empty
df are returned. If there was nog connection with the API an NULL is returned

```{r municipality}
# Example 1: municipality
muni_code <- "200"
muni_data_example_1 <- GetSamenMetenAPIinfoMuni2(muni_code)

# Example 2: error in input
muni_code <- 200
muni_data_example_2 <- GetSamenMetenAPIinfoMuni2(muni_code)

# # Example 3: error in unknown municipality
muni_code <- "908354" 
muni_data_example_3 <- GetSamenMetenAPIinfoMuni2(muni_code)

```
## Get the sensors of a project
You can use the function 'GetSamenMetenAPIinfoProject2' to obtain for a particular
project, all the sensors and their meta information. The meta
information contains the name (kit_id), the location(lat, lon), some names of
the reference stations. A second dataframe is returned including information
about which parameters are measured, their units and the url to the
observations.

NOTE: the input for the function is the name of the project, as a string.
NOTE: If connection with API was succesful, but no data available, then an empty
df are returned. If there was nog connection with the API an NULL is returned

An overview of all the projectnames can be found in the github for Samen Analyseren Tool

```{r project}
# Example 1: project
project_name <- "HEI"
project_data_example_1 <- GetSamenMetenAPIinfoProject2(project_name)

# Example 2: error input
project_name <- 200
project_data_example_2 <- GetSamenMetenAPIinfoProject2(project_name)

# Example 2: error unknown project
project_name <- "hei"
project_data_example_2 <- GetSamenMetenAPIinfoProject2(project_name)

```
## Get the data (observations) of a sensor
Each sensor (kit_id) can contain multiple sensors, each measuring a parameter
such as PM2.5 or Temperature. For each parameter a datastream is stored in the
Samen Meten API. To obtain the data from 1 parameter the function below can be
used. The datastream_id is given in the GetSamenMetenAPIinfo-functions.

NOTE: to get the observations from the API can take some time. Consider to split
the time period in shorter periods

```{r Obtain data observations}
datastream_id <- "31508"
kit_id <- "LTD_55101"
ymd_from <- "20220101"
ymd_to <- "20220110"

observations_1 <- GetSamenMetenAPIobs2(datastream_id, kit_id ,ymd_from, ymd_to)
``` 

```{r Obtain data observations after info}
# You can use the info from 'project_data_example_1' 
datastream_id <- project_data_example_1$datastream_data$datastream_id[[1]]
kit_id <- project_data_example_1$datastream_data$kit_id[[1]]
ymd_from <- "20220101"
ymd_to <- "20220110"

observations_2 <- GetSamenMetenAPIobs2(datastream_id, kit_id ,ymd_from, ymd_to)
``` 
