---
title: "example_GetSamenMetenData"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example_GetSamenMetenData}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(samanapir)
```

# Introduction

The sensor data from [Samen Meten][https://samenmeten.rivm.nl/dataportaal/] can
be obtained using an API. This package contains functions to use this API. First
part is to get the sensors in a particular project or municipality and thir
meta-data. Second get the observations of 1 parameter of the sensor for a
particular time period.

For more information about the API see: [API Samen Meten][https://www.samenmetenaanluchtkwaliteit.nl/dataportaal/api-application-programming-interface]

## Get the sensors of a municipality
You can use the function 'GetSamenMetenAPIinfoMuni' to obtain for a particular
municipality, all the sensors and their meta information. The meta
information contains the name (kit_id), the location(lat, lon), some names of
the reference stations. A second dataframe is returned including information
about which parameters are measured, their units and the url to the
observations.

NOTE: the input for the function is the code of the municipality, as a string.

```{r municipality}
# Example 1: municipality
muni_code <- "200"
muni_data_example_1 <- GetSamenMetenAPIinfoMuni(muni_code)

# Example 2: error in input
muni_code <- 200
muni_data_example_2 <- GetSamenMetenAPIinfoMuni(muni_code)

# # Example 3: error in unknown municipality
# muni_code <- "908354" 
# muni_data_example_3 <- GetSamenMetenAPIinfoMuni(muni_code)

```
## Get the sensors of a project
You can use the function 'GetSamenMetenAPIinfoProject' to obtain for a particular
project, all the sensors and their meta information. The meta
information contains the name (kit_id), the location(lat, lon), some names of
the reference stations. A second dataframe is returned including information
about which parameters are measured, their units and the url to the
observations.

NOTE: the input for the function is the name of the project, as a string.

An overview of all the projectnames can be found in the github for Samen Analyseren Tool

```{r project}
# Example 1: project
project_name <- "HEI"
project_data_example_1 <- GetSamenMetenAPIinfoProject(project_name)

# Example 2: error input
project_name <- 200
project_data_example_2 <- GetSamenMetenAPIinfoProject(project_name)

# # Example 2: error unknown project
# project_name <- "hei"
# project_data_example_2 <- GetSamenMetenAPIinfoProject(project_name)

```
## Get the data (observations) of a sensor

Each sensor (kit_id) can contain multiple sensors, each measuring a parameter
such as PM2.5, Temperature. For each parameter a datastream is stored in the
Samen Meten API. To obtain the data from 1 parameter the function below can be
used. The datastream_id is given in the GetSamenMetenAPIinfo-functions.

NOTE: to get the observations from the API can take some time. Consider to split
the time period in shorter periods


```{r Obtain data observations}
datastream_id <- "31508"
kit_id <- "LTD_55101"
ymd_from <- "20220101"
ymd_to <- "20220110"

observations_1 <- GetSamenMetenAPIobs(datastream_id, kit_id ,ymd_from, ymd_to)
``` 

```{r Obtain data observations after info}
# You can use the info from 'project_data_example_1' 
datastream_id <- project_data_example_1$datastream_data$datastream_id[[1]]
kit_id <- project_data_example_1$datastream_data$kit_id[[1]]
ymd_from <- "20220101"
ymd_to <- "20220110"

observations_2 <- GetSamenMetenAPIobs(datastream_id, kit_id ,ymd_from, ymd_to)
``` 
