---
title: "example_GetLMLData"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example_GetLMLData}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(samanapir)
```

# Introduction

The reference data from [Luchtmeetnet][https://www.luchtmeetnet.nl/] can
be obtained using an API. This package contains functions to use this API.

For more information about the API see: [API Luchtmeetnet][https://api-docs.luchtmeetnet.nl/]

## Information about a specific station
With the function 'GetLMLstatinfoAPI2', you can obtain the metadata of the station,
like location and name.

```{r Station information}
# Get station information
station_info <- GetLMLstatinfoAPI2("NL01908")

```
## Information of all stations
You can also obtain the metadata of all stations in once.
```{r All stations informtation}
all_stations <- GetLMLallstatinfoAPI2()
```

## Data from specific station
The measurements from a specific station can be gathered for a given time period.
This will return all the measured components (e.g. PM, NO2)
```{r data from specific station}
data_station <- GetLMLstatdataAPI2("NL49012", "20260205", "20260215")
```

## Data and info for a specific station
In order to get the data and the info from a specific station, you can use this,
whixh combines the function above.
```{r}
combined_station <- GetLMLAPI2("NL49012", "20260505", "20260510")
```
