---
title: "example_GetKNMIData"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example_GetKNMIData}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(samanapir)
```

# Introduction

The meteo data from [KNMI][https://www.knmi.nl/] can
be obtained using an API. This package contains two functions to use their data.
We used two different ways to obtain the data, one with and without an API-key. 
This API-key can be get on: [register for KNMI][https://developer.dataplatform.knmi.nl/register/]

You can also use the anonymous key: [get anonymous key][https://developer.dataplatform.knmi.nl/open-data-api#token]

We store the key in the system:
```{r}
Sys.setenv(KNMI_API_TOKEN = "Put_your_key_here"
)
```

For more information about the API and information about the data see: [API KNMI][https://dataplatform.knmi.nl/dataset/10-minute-in-situ-meteorological-observations-1-0]

The other method we use this: [KNMI daggegevens][https://www.knmi.nl/kennis-en-datacentrum/achtergrond/data-ophalen-vanuit-een-script]

## Information about the parameters measured
```{r parameter information}
all_parameters <- getKNMIparameters(token = Sys.getenv("KNMI_API_TOKEN"))

```

## Get wind data
For the Analyse Together tool we are only interested in the wind data. So this function
will only retrieve those measurements.

Furthermore there is the options for the hourly mean. Use 'data_result = "hourly"'.

The wind direction is parameter "dd",  wind speed is parameter "ffs"
```{r wind data}
winddata <- GetKNMIAPIEDR(date_start = "2026-05-01",
                                 date_end  = "2026-05-02",
                                 token = Sys.getenv("KNMI_API_TOKEN"),
                                 location_id = c("356"),
                                 parameter = "wind",
                                 data_result = "hourly")
```
## Using other API: hourly values
This is another access to the same data, without key. In this function you can 
also get the data from multiple stations in the same call.

NB: this are the average hourly values
```{r}
  # initialisatie
  stations <- c('260', '248')
  ymd_vanaf = 20191214
  ymd_tot = 20191215

  # Get the data
  knmi_data <- GetKNMIAPI2(stations, ymd_vanaf, ymd_tot )

```
